In-Rank mesh optimization for URL customized promotion in SEO

### 2015-03-03 MY_PAPERS/article_sduprey_iswag_02_06_2014.tex
iswag

search engine, e-commerce, page rank, in rank, mesh optimization, global optimization

@@

We use open source tools Apache Hadoop \cite{map_reduce} and Apache Spark \cite{spark_methodo} to solve these big data problems in a scalable way. 

@@

In contrast to Hadoop's two-stage disk based Map/Reduce paradigm, Spark's in-memory primitives provide the needed performance (see \cite{spark_methodo_bis} \cite{spark_methodo}).
By allowing user programs to load data into a cluster's memory and query it repeatedly, Spark is well suited for our purpose \cite{incremental_ram}
\cite{spark_bis_bis}.

@@

Our internal mesh is stored in Neo4j (\cite{neo4j}. It allows us to solve analytical problems

>>>>

search engine, e-commerce, page rank, in rank, mesh optimization, global optimization, Hadoop, Spark GraphX, Neo4j

@@

We use open source tools Apache Hadoop \cite{apache_hadoop} and Apache Spark \cite{spark} to solve these big data problems in a scalable way. 

@@

In contrast to Hadoop's two-stage disk based Map/Reduce paradigm, Spark's in-memory primitives provide the needed performance.
By allowing user programs to load data into a cluster's memory and query it repeatedly, Spark is well suited for our purpose (\cite{incremental_ram} and
\cite{spark_methodo}).

@@

Our internal mesh is stored in Neo4j \cite{neo4j}. It allows us to solve analytical problems
